Summary of models

### 2022-07-20 Models.Rmd
correlation and summary of models

```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
library(knitr)
library(dplyr)
library(kableExtra)
library(tidyverse)
#install.packages("broom.mixed")
library(broom.mixed)
library(broom)
#install.packages("lmerTest")
library(lmerTest)

@@

@@

@@

@@

@@

@@

>>>>

@@

## Hymenoptera visitation

#Models _ fruit proportion 
# hymenoptera visitation
ta_f4<-Pollinator_Plant %>%
  nest_by(Plant_gen_sp) %>%
  mutate(model = list(glmer(cbind(fruit_formado, Fruit_No)~Hym_visit + (1|Site_ID),family=binomial,data)))%>%
  summarise(broom.mixed::tidy(model)) %>%
  ungroup()

ta_f4<-ta_f4 %>%
  select(-effect, -group)  %>%
  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))

ta_f4<-filter(ta_f4, !term == "sd__(Intercept)")

ta_f4 %>% 
    kable("latex",booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
column_spec(6, bold = ifelse(ta_f4$p.value < 0.05, T, F) )%>%
  kable_styling(position="center", latex_option="hold_position")

@@

\newpage
## Hymenoptera visitation
```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
Pollinator_Plant<- read.csv("Data/Pollinator_Plant.csv") 
Pollinator_Plant<-Pollinator_Plant[,-1]

# hymenoptera visitation
ta_seed4<-Pollinator_Plant %>%
  nest_by(Plant_gen_sp) %>%
  mutate(model = list(lmer(Seeds~Hym_visit+(1|Site_ID),data))) %>%
  summarise(broom.mixed::tidy(model)) %>%
  ungroup()

ta_seed4<-ta_seed4 %>%
  select(-effect, -group)  %>%
  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))

ta_seed4<-filter(ta_seed4, !term == "sd__(Intercept)" & !term =="sd__Observation")

ta_seed4 %>% 
kable("latex", booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
column_spec(7, bold = ifelse(ta_seed4$p.value < 0.05, T, F) )%>%
  kable_styling(position="center", latex_option="hold_position")

@@

## Hymenoptera visitation
```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
Pollinator_Plant<- read.csv("Data/Pollinator_Plant.csv") 
Pollinator_Plant<-Pollinator_Plant[,-1]

#Models _ Seed weight 
# Hymenoptera visitation
ta_weight4<-Pollinator_Plant %>%
  nest_by(Plant_gen_sp) %>%
  mutate(model = list(lmer(Seed_weight~Hym_visit+(1|Site_ID),data))) %>%
  summarise(broom.mixed::tidy(model)) %>%
  ungroup()

ta_weight4<-ta_weight4 %>%
  select(-effect, -group)  %>%
  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))

ta_weight4<-filter(ta_weight4, !term == "sd__(Intercept)" & !term =="sd__Observation")

ta_weight4 %>% 
kable("latex", booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
column_spec(7, bold = ifelse(ta_weight4$p.value < 0.05, T, F) )%>%
  kable_styling(position="center", latex_option="hold_position")

@@

## Fruit proportion - hymenoptera visitation

# hymenoptera visitation
ta_f4_la<-lavan_tog %>%
  nest_by(Plant_gen_sp) %>%
  mutate(model = list(glmer(cbind(fruit_formado, Fruit_No)~Hym_visit + (1|Site_ID),family=binomial,data)))%>%
  summarise(broom.mixed::tidy(model)) %>%
  ungroup()

ta_f4_la<-ta_f4_la %>%
  select(-effect, -group)  %>%
  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))

ta_f4_la<-filter(ta_f4_la, !term == "sd__(Intercept)")

ta_f4_la %>% 
    kable("latex",booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
column_spec(6, bold = ifelse(ta_f4_la$p.value < 0.05, T, F) )%>%
  kable_styling(position="center", latex_option="hold_position")

@@

## Seed number - hymenoptera visitation

# hymenoptera visitation
ta_seed4_la<-lavan_tog %>%
  nest_by(Plant_gen_sp) %>%
  mutate(model = list(lmer(Seeds~Hym_visit+(1|Site_ID),data))) %>%
  summarise(broom.mixed::tidy(model)) %>%
  ungroup()

ta_seed4_la<-ta_seed4_la %>%
  select(-effect, -group)  %>%
  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))

ta_seed4_la<-filter(ta_seed4_la, !term == "sd__(Intercept)" & !term =="sd__Observation")

ta_seed4_la %>% 
kable("latex", booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
column_spec(7, bold = ifelse(ta_seed4_la$p.value < 0.05, T, F) )%>%
  kable_styling(position="center", latex_option="hold_position")

@@

## Seed weight - hymenoptera visitation

# hymenoptera visitation
ta_weight4_la<-lavan_tog %>%
  nest_by(Plant_gen_sp) %>%
  mutate(model = list(lmer(Seed_weight~Hym_visit+(1|Site_ID),data))) %>%
  summarise(broom.mixed::tidy(model)) %>%
  ungroup()

ta_weight4_la<-ta_weight4_la %>%
  select(-effect, -group)  %>%
  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))

ta_weight4_la<-filter(ta_weight4_la, !term == "sd__(Intercept)" & !term =="sd__Observation")

ta_weight4_la %>% 
kable("latex", booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
column_spec(7, bold = ifelse(ta_weight4_la$p.value < 0.05, T, F) )%>%
  kable_styling(position="center", latex_option="hold_position")
